Verifying Demonstrations

### 2018-11-01 paper/analysis-performance.tex
Minor edits in intro (only labels in other files)
update of privacy and performance

\section{Performance and implementation}

\subsection{Implementation on smartphones or smart-cards}
Technological progress has enabled more advanced cryptography on Smart-cards and Smartphones which could be used to implement our solution : Benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in  \SI{153}{\milli\second}. However, those benchmarks also demonstrate that SmartCards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). While the limited processing power of many embarked systems has been a challenge, Idemix has been succesfully implemented to prove the posession of credentials on Java Cards by Bichsel et al. in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation « suitable for real life transactions »~\cite{IRMA} while maintaining security and privacy for its users.

\subsection{Threshold of witnesses}

Assume that every person has 5000 contacts in their contact 
book~\cite{DifficultyOfPrivateContactDiscovery}.
Then it would be reasonable to set the threshold of at least 6000 witnesses.
According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
\SI{2.66}{\giga\hertz} Core 2 processor.
This yields \(
  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
  \SI{48}{\second}.
\) of processing.

>>>>

\section{Performance and implementation}
\label{PerformanceAnalysis}

Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and
computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
The first step is only done once and is fairly costly in terms of ressources. 
This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
This can be reduced to 4 random number generations and one exponentiation using precomputation.
The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
%subscriptions. IEEE Security & Privacy, (1), 1.

%\paragraph{Threshold of witnesses.}
%Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
%Then it would be reasonable to set the threshold of at least 6000 witnesses.
%According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
%signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
%\SI{2.66}{\giga\hertz} Core 2 processor.
%This yields \(
%  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
%  \SI{48}{\second}.
%\) of processing.

### 2018-11-01 paper/privacy-properties.tex
update of privacy and performance

In addition to the verification requirements, we also need to define the 
privacy properties.
In voting protocols, there are mainly three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can 
    be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
    the vote was cast in any particular way.
\end{description}

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against 
her will.
Receipt freeness, while desirable at first glance, is not desirable
here as, in contrast to voting, receipt freeness for \emph{how} the
voter voted (\ie the cause of the protest) implies receipt freeness
for \emph{that} the voter voted (\ie the protester was there) which
conflicts with verifiability.  
%For instance, the location proof might be useful to prove presence to a third 
%party, \eg for strengthening the authenticity of witness information.

Thus privacy remains.
For the protester we want unlinkability between a protester's real identity 
\(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace will not be able to tell if it belongs to 
Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's, she should not 
be able to link another proof (\eg, from a different protest) as a consequence.

\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
location \(l\) against an adversary who is not present in the location.
Due to the limitations of physical space, two individuals present in the same 
location will inevitably learn of each other's presence.
Thus we will only try to prevent individuals who are not present to learn of 
this presence.}

@@

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Moreover, any temporary identifiers such as pseudonyms may only be
reused when strictly necessary for the fulfillment of verifiability
properties listed in \label{verifiability-properties} to prevent
inference on long-term identities by repeated samples and side information.

>>>>

In addition to the verification requirements, we also need to define the privacy properties.
In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can 
    be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
    his vote was cast in any particular way.
\end{description}

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.

Thus, in our context the crucial property is therefore privacy.
More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).

%Seb: I have put it in comments to save on space
%\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
%location \(l\) against an adversary who is not present in the location.
%Due to the limitations of physical space, two individuals present in the same 
%location will inevitably learn of each other's presence.
%Thus we will only try to prevent individuals who are not present to learn of 
%this presence.}

@@

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Finally, any temporary identifiers such as pseudonyms should only be reused when strictly necessary for the fulfillment of verifiability properties listed in \label{verifiability-properties} to prevent inference on long-term identities by repeated samples and side information.
